[weapon_reload]
infinite_ammo_primary 	= true			;Infinite ammo for main weapons
infinite_ammo_secondary = true			;Infinite ammo for Pistols

[lios]
enable 		= true							;Look Into Opticial Scope
range_add 	=  0.6							;Percent increase to NPC range
fov_add		= -0.4							;Percent increase to NPC FOV (negative to reduce)

[npc_help]
enable = true						; Enables NPC informing allies of your location
npc_help_distance_close = 25		; Sets distance that an NPC who has "seen" the player can alert other NPC's to the players location. Value is distance squared
npc_help_timer_close = 10000			; Sets time before the NPC inform allies in ms
npc_help_distance_medium = 625 
npc_help_timer_medium = 15000
npc_help_distance_far = 1600
npc_help_timer_far = 30000

[ghillie_settings]
enable = true   				; Enables reduced detection of the Ghillie Suit.
detect_range_factor = 0.30 		; Factor of eye_range that a NPC no longer ignores a player in a Ghillie
help_distance_factor = 0.6		; Factor for Decreasing Distance for NPC's informing allies of your position if you are wearing a Ghillie. Used in conjuction with npc_help
help_timer_factor = 3.0			; Factor for Increasing Timer for NPC's informing allies of your position if you are wearing a Ghillie. Used in conjunction with npc_help
aim_time_factor = 3.0			; Multiplier for time it take for NPC's to aim while wearing a Ghillie

[night_settings]
enable = true
detect_range_factor = 0.80				; Factor of range that a NPC no longer ignores a player at during night. (10pm to 3am)
help_distance_factor = 0.8				; Factor for Decreasing Distance for NPC's informing allies of your position during night hours. Used in conjuction with npc_help
help_timer_factor = 2.0					; Factor for Increasing Timer for NPC's informing allies of your position during night hours. Used in conjunction with npc_help
aim_time_factor = 1.5					; Multiplier for time it take for NPC's to aim during night hours

[recon_settings]
enable = true
detect_range_factor = 0.70				; Factor of range that a NPC no longer ignores a player if he is Recon during night. (10pm to 3am)
help_distance_factor = 0.75				; Factor for Decreasing Distance for NPC's informing allies of your position during night hours as Recon. Used in conjuction with npc_help
help_timer_factor = 2.5					; Factor for Increasing Timer for NPC's informing allies of your position during night hours Recon. Used in conjunction with npc_help
aim_time_factor = 1.4					; Multiplier for time it take for NPC's to aim during night hours as recon